### 2019-05-22 thesis.tex
Minor additions

\chapter{Theoretical framework}
\label{cha:theo-fram}
Let us consider a given set of atoms or molecules, which is composed of
positively and negatively charged particles, and also neutral components.
One can say, correctly, that such a system is an ionized gas, because of
the presence of charged particles in its composition. However, what can
be said about the dominant dynamics of the ionized gas, since neutral and
charged particles have quite a distinct behavior? Assuming the gravitational
force is negligible, the neutral particles will move freely in the medium
until one collides with another \cite{chen}. Thus, the interaction between
the neutral components is characterized as short-ranged, since it relies
only on binary collisions.

>>>>

\chapter{Theoretical framework}
\label{cha:theo-fram}
Let us consider a given set of atoms or molecules, which is composed of
positively and negatively charged particles, and also neutral components.
One can say, correctly, that such a system is an ionized gas, because of
the presence of charged particles in its composition. However, what can
be said about the dominant dynamics of the ionized gas, since neutral and
charged particles have quite a distinct behavior? Assuming that the
gravitational force is negligible, the neutral particles will move freely
in the medium until one collides with another \cite{klimon}. Therefore, the
interaction between the neutral components is characterized as short-ranged,
since it relies only on collisions between two particles. Charged particles,
on the other hand, are sources of electric fields. Besides that, their
motion generates currents that will induce magnetic fields. The
